Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
write introduction, and some other adjustments

\usepackage{multicol}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage{mathtools}
\usepackage{cuted}
\usepackage{makecell}

@@

\section{Introduction}
\label{sec:intro}
The introduction \dots

@@

Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
The original dataset contains 3 classes $A_1, A_2$, and $A_3$, and we are able to decompose each into some subclasses, e.g., $A_1$ is decomposed into two subclasses of samples $A_{11}$ and $A_{12}$.
There are 4 binary classifiers, each determines whether a sample belongs to the union of some subclasses marked with boxes, e.g., $d_1$ determines whether a sample belongs to the union of $\{A_{11}, A_{12}, A_{21}, A_{22}\}$.
We can use classifiers $d_1, d_2, d_3$ and set operations for the classification task:
\begin{itemize}
	\item $d_1 - (d_2 + d_3)$ determines samples belong to $A_1$;
	\item $d_1 \cdot d_2 + d_3$ determines samples belong to $A_2$;
	\item $d_2 - d_1$ determines samples belong to $A_3$.
\end{itemize}
For the partial classification task of class $A_3$, it suffices to use only $d_2$ and $d_4$ and their intersection $d_2 \cdot d_4$ to determine samples in $A_3$.

\subsection{Our Work}

@@

Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

% \linespread{1.1}
\begin{figure}[h]
	\begin{tabular}{|c|c|cccc|}
	\cline{1-6}
	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
	\end{tabular}
	\caption{Encoding for the Intro Example}
	\label{fig:assemble-example-encoding}
\end{figure}
% \linespread{1.0}

@@

\begin{algorithm}[h]
	\caption{The General Algorithm}
	\label{tab:heuristic-search}
	\begin{algorithmic}[1]
		\Require The inputs to the assembly problem;
		\Ensure $D$, a classifier set satisfying constraints, or $\emptyset$ if not feasible.
		\State $Q \gets \emptyset$; \Comment A priority queue, the last element $h$ is the key
		\Function{Expand}{$D$} \Comment $D$, the classifier set
			\For{$d \in \mathcal{D} - D$}
				\State Calculate the encoding $C$ using $D \cup \{d\}$;
				\State Calculate the entropy $h$ for $C$;
				\State $Q \gets Q \cup \{(D \cup \{d\}, C, h)\}$;
			\EndFor
		\EndFunction
		\Function{HeuristicSearch}{}
			\State $\Call{Expand}{\emptyset}$;
			\While{$Q \neq \emptyset$}
				\State $(D, C, h) \gets Pop(Q)$;
				\If{$e_0 == 0$}
					\State \Return $D$;
				\EndIf
				\If{|D| < k}
					\State $\Call{Expand}{D}$;
				\EndIf
			\EndWhile
			\State \Return $\emptyset$;
		\EndFunction
	\end{algorithmic}
\end{algorithm}

The search is guided by the residual entropy \eqref{eq:entropy} of target subclasses and dummy subclasses.
\begin{equation}
	H(C) = \sum_{c \in C} p(c)H(c) = \sum_{c \in C} p(c)\sum_{l \in \mathcal{L}'} p(c, l)\log\frac{1}{p(c, l)}
	\label{eq:entropy}
\end{equation}
where $p(c)$ is the probability for encoding $c$ to occur, and $p(c, l)$ is the probability of a sample having encoding $c$ and label $l$.
Note that the label ranges over $\mathcal{L}'$, the set of target labels and one dummy label, and all labels that are not target is defined to be equal to the dummy one.
In each search iteration, the algorithm will choose the classifier set that minimizes the entropy greedily, so that the search could possibly to end with minimum search depth.

@@

The results shows we can derive a good basis of binary classifers through these clusters. First, the good mapping from cluster to class label means we can use these binary classifiers to construct subclasses mentioned in the beginning of this section. The fact that gate vectors from different models varies will prevent the trival case that cluster one-to-one map to class label, leading to substantial reduction on number of model parameters.

@@

Afterwards we modify the network architecture of fully connected layers to form a binary classifer $g_{\theta'}(\cdot)$. The reason to do this includes:
\begin{itemize}
	\item It has less parameters than 100-class classifers.
	\item It is easier to train, i.e. easier to have higher accuarcy.
	\item Weights of convolution layers in the orginal model could be reused. We just need to finetune the model without running long sessions to train from scratch.
\end{itemize}

@@

\section{Experiments}
\subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
In this section, we perform K-Means on the CDRP control gates of each sample. For each cluster, we get a binary-classifier to determine whether the test sample should be in the cluster. Then, we fine tune each classifier in the CIFAR-100 dataset.

\paragraph{Clusters.} For VGGNet, we generate $1.5$ clusters per class.
Then, we get $14$ clusters from $5$ classes, among which $7$ clusters are from VGG16-C and $7$ clusters from VGG16-D.

@@

\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifer. Each classifier judges whether the test sample should in the corresponding cluster. 
From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.

@@

Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $pr$ i.e. if $pr=0.9$, $90\%$ of channels in all layers are pruned. 
As a result, each classifer only has $10\%$ parameters of the original full network.

\paragraph{Finetune.} The classifiers we get above cannot achieve any meaningful results because they tend to classifiy all test samples not in the cluster and the weights of the last layer is initialized randomly.
We implement finetune on these classifers to make the results more meaningful and accurate. 
Since the negative samples are greatly more than positive ones in the dataset, we need to implement some strategies to balance them i.e. in each iteration we ensure the ratio of positive and negative samples is about $1:1$ in the batch.

We train each classifer with $1500$ iterations with a batch size $200$. 
The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
We only train the pruned model i.e. weights of the pruned channels will remain zero.
With a prune ratio $pr\leq0.9$, most of the classifers can reach an accuracy more than 80\% after finetune, which is much higher than the overall accuracy of the original full network.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
In this section, we implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. According to the 0/1 result of each classifer, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.

\paragraph{Fusion}We implement Algorithm~\ref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this Algorithm~\ref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers with different prune ratio is shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[h]

    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifer-accuracy}
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Classifier ID & 3 & 4 & 1 & 2 \\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
	\hline
	\end{tabular}
\end{table}

\paragraph{Verifying Result.}By combining the 0/1-results of the four classifiers, we can determine the class label unqiuely of one test sample.
For example, if the result of classifer-3 is $0$ whether results of others are all $1$s, the encoding will be $0111$ and we can determine the sample is in class $0$.

Actually, we can determine the class uniquely with the prefix of encodings. 
For instance, if the result of classifer-3 is $0$, we don't need to take other classifers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}

@@

\begin{table}[h]

    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline

	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\

	\hline
	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
	\hline
	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\

	\hline

	\end{tabular}
\end{table}

From Table~\ref{tab:encoding-and-accuarcy}, we find the overall accuracy is quite high if prune ratio $pr\leq0.9$ while the accuracy drops dramatically when $pr=0.95$ since we prune too much channels or even destroy the connectivity of the network. 
When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.

Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency. 
When $pr=0.9$, we can infer with the $4$ binary-classifiers in parallel instead of applying the original network, which can save about $90\%$ computing consumption on a single device as well as improve the accuracy.

>>>>

\usepackage{multicol}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage{mathtools}
\usepackage{cuted}

@@

\section{Introduction}
\label{sec:intro}
The development of deep learning has proved its great capability, and it will be more beneficial if we can plant deep learning models into edge devices like wearable devices.
However, the limited energy supply and computational capability of edge devices lead to constraints on the scale and complexity of deep neural networks.
The edge devices often need only to perform very specific tasks, whereas the pre-trained models deals with more general cases.
This makes it possible to develop task-specific and light-weighted models to meet various constraints of edge device.

% Network fusion is a potential way to further improve the performance of network models with the advance of edge devices, where we could deploy many models through devices, let them perform inference in parallel, and retrieve and join the results \cite{fang2019teamnet}.
% Nevertheless, this could cause redundant complexity across models, making it unable to fully utilize the capability of each edge devices.

In this paper, we first study a framework of assembling multiple small binary classifiers into one that performs complicated classification tasks.
Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.

@@

The original dataset contains 3 classes $A_1, A_2$, and $A_3$, and we are able to decompose each into some subclasses, e.g., $A_1$ is decomposed into two subclasses of samples $A_{11}$ and $A_{12}$.
There are 4 binary classifiers, each determines whether a sample belongs to the union of some subclasses marked with boxes, e.g., $d_1$ determines whether a sample belongs to the union of $\{A_{11}, A_{12}, A_{21}, A_{22}\}$.
We can use classifiers $d_1, d_2, d_3$ and set operations for the classification task:
\begin{itemize}
	\item $d_1 - (d_2 + d_3)$ determines samples belong to $A_1$;
	\item $d_1 \cdot d_2 + d_3$ determines samples belong to $A_2$;
	\item $d_2 - d_1$ determines samples belong to $A_3$.
\end{itemize}
For the partial classification task of class $A_3$, it suffices to use only $d_2$ and $d_4$ and their intersection $d_2 \cdot d_4$ to determine samples in $A_3$.

We then instantiate such framework in a concrete setting of image classification.
To do so, we need to find a desirable initial set of binary classifiers which is not costly to obtain but also guarantees non-trivial solutions.
We use critical data routing path (CDRP) method \cite{wang2018interpret} and clustering of CDRPs to extract from multiple large networks to find those classifiers with reduced complexity, and then apply the assembly framework to build task-specific model.
Such CDRP model decomposition and assembly framework has many applications.
\begin{itemize}
	\item Fuse networks at a fine-grained level.
	In the CDRP decomposition, we may use only relevant convolution kernels in the resulting classifiers.
	Therefore we can skip redundant feature extractors instead of fusing entire networks by concatenating their outputs.
	\item Fused networks may be trained on different datasets (but with the same task), and we can also use dataset different from the ones models are trained on as the basis of CDRP decomposition and assembly.
	The resulting model will be able to cover tasks performed on the new dataset.
\end{itemize}

In this paper, we address the followings.
\begin{itemize}
	\item We propose a general assembly framework for binary classifiers and a heuristic algorithm to the search problem in \cref{sec:assembly}.
	\item We instantiate the assembly framework based on the CDRP method for the image classification task on CIFAR-100 in \cref{sec:cdrp}.
	\item We experiment such implementation on a subset of CIFAR-5 in \cref{sec:experiments}.
\end{itemize}

@@

% \linespread{1.1}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.55\linewidth]{fig/encoding_example.png}
	% \begin{tabular}{|c|c|cccc|}
	% \cline{1-6}
	% \multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
	% \multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
	%  & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
	% \multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
	%  & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
	%  & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
	% $A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
	% \end{tabular}
	\caption{Encoding for the Intro Example}
	\label{fig:assemble-example-encoding}
\end{figure}
% \linespread{1.0}

Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
If we only use the encoding from $d_1, d_2, d_3$ in the orange box, no two subclasses with different labels share the same encoding, and therefore it certifies the correctness of the feasible solution proposed before.
For the partial classification task for $A_3$, using two bits from $d_2, d_4$ in the blue box already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.

@@

\begin{algorithm}[h]
    \caption{The Heuristic DFS Algorithm}
    \label{tab:heuristic-search}
    \begin{algorithmic}[1]
      \Require The inputs to the assembly problem;
      \Ensure $D$, a classifier set satisfying constraints, or $\emptyset$ if not feasible.
      \Function{HeuristicSearch}{$D$}
        \State $Q \gets \emptyset$; \Comment An array of descendent states
        \For{$d \in \mathcal{D} - D$}
          \State Calculate the encoding $C$ using $D \cup \{d\}$;
          \State Calculate the entropy $h$ for $C$;
          \State $Q \gets Q \cup \{(D \cup \{d\}, C, h)\}$;
        \EndFor
        \State Sort $Q$ by ascending entropy;
        \For{$(D, C, h) \in Q$}
          \If{$h == 0$}
            \State \Return $D$; \Comment Find a hit if residual entropy is 0
          \EndIf
          \If{|D| < k}
            \State $\Call{HeuristicSearch}{D}$; \Comment Search deeper level
          \EndIf
        \EndFor
        \State \Return $\emptyset$;
      \EndFunction
    \end{algorithmic}
\end{algorithm}

The search is guided by the residual entropy \eqref{eq:entropy} of target subclasses and dummy subclasses.
\begin{equation}
	H(C) = \sum_{c \in C} p(c)H(c) = \sum_{c \in C} p(c)\sum_{l \in \mathcal{L}'} p(c, l)\log\frac{1}{p(c, l)}
	\label{eq:entropy}
\end{equation}
where $p(c)$ is the probability for encoding $c$ to occur, and $p(c, l)$ is the probability of a sample having encoding $c$ and label $l$.
Note that the label ranges over $\mathcal{L}'$, the set of target labels and one dummy label, and all labels that are not targets are defined to be equal to the dummy one.
In each search iteration, the algorithm will choose the classifier set that minimizes the entropy greedily, so that the search could possibly to end with minimum search depth.

@@

The results shows we can derive a good basis of binary classifiers through these clusters. First, the good mapping from cluster to class label means we can use these binary classifiers to construct subclasses mentioned in the beginning of this section. The fact that gate vectors from different models varies will prevent the trival case that cluster one-to-one map to class label, leading to substantial reduction on number of model parameters.

@@

Afterwards we modify the network architecture of fully connected layers to form a binary classifier $g_{\theta'}(\cdot)$. The reason to do this includes:
\begin{itemize}
	\item It has less parameters than 100-class classifiers.
	\item It is easier to train, i.e. easier to have higher accuarcy.
	\item Weights of convolution layers in the orginal model could be reused. We just need to finetune the model without running long sessions to train from scratch.
\end{itemize}

@@

\section{Experiments}
\label{sec:experiments}
\subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
\paragraph{Clusters.} We perform K-Means on the CDRP control gates of each sample. 
For VGGNet, we generate $1.5$ clusters per class.
Then, we get $14$ clusters from $5$ classes, among which $7$ clusters are from VGG16-C and $7$ clusters from VGG16-D.

@@

\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifier. Each classifier judges whether the test sample should in the corresponding cluster. 
From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.

@@

Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
As a result, each classifier only has $10\%$ parameters of the original full network.

\paragraph{Finetune.} The classifiers we get above cannot achieve any meaningful results because they tend to classifiy all test samples not in the cluster and the weights of the last layer is initialized randomly.
We implement finetune on these classifiers to make the results more meaningful and accurate. 
Since the negative samples are greatly more than positive ones in the dataset, we need to implement some strategies to balance them i.e. in each iteration we ensure the ratio of positive and negative samples is about $1:1$ in the batch.

We train each classifier with $1500$ iterations with a batch size $200$. 
The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
We only train the pruned model i.e. weights of the pruned channels will remain zero.
After finetune, most of the classifiers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.

\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
The accuracy of the four classifiers are shown in Table~\ref{tab:classifier-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.

\begin{table}[h]
    \caption{Accuracy of Chosen Binary-Classifiers}
    \label{tab:classifier-accuracy}
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	Classifier ID & 3 & 4 & 1 & 2 \\
	\hline
	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
	\hline
	\end{tabular}
\end{table}

\paragraph{Verifying Result.}By combining the 0/1-results of the four classifiers, we can determine the class label unqiuely of one test sample.
For example, if the result of classifier-3 is $0$ whether results of others are all $1$s, the encoding will be $0111$ and we can determine the sample is in class $0$.

Actually, we can determine the class uniquely with the prefix of encodings. 
For instance, if the result of classifier-3 is $0$, we don't need to take other classifiers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}

@@

\begin{table}[h]
    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{|c|c|c|c|c|c|c|}
	\hline
	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\hline
	Encoding &0 & 110 & 1110 &10 & 1111 &\\
	\hline
	\end{tabular}
\end{table}
